\subsection{System Components}
	\subsubsection{Introduction}
		The system, as a whole, can essentially be broken down into a combination of many smaller tasks. These tasks are then able to be grouped together based upon their dependency with one another - we shall call these components. This process is often known as decomposition.
		
		Decomposition allows the programmer to then interact with these smaller, decoupled components as a black-box - as they are only required to be knowledgeable of the interface, rather than the implementation. This is highly beneficial when a working on larger projects, as a team, where it is not very feasible for each programmer to be well-versed regarding the logic involved in the solutions for each task required by the system.
		
		Another note-worthy benefit of decomposition, is that it unlocks the ability for your components to be designed in such a way that they can integrated into other projects - this is known as reusability. The appeal of this idea expands further when we consider that some of these components our system would require have already been created, and submitted, for anybody to use freely. This is one of the major drives in open-source software.
		
		Decomposition plays a key role in many programming languages. For example, most popular programming languages - such as C++, Java and Python - feature some implementation of the object-oriented paradigm. Object-oriented programming provides the programmer with the tools to abstract from the logic involved in using the solutions to particular tasks.
		
		In order for us to efficiently create a robust and manageable system, it is not only critical that we carefully consider all of the individual components that are required. But that we also deeply explore the various design patterns available to us and how we can integrate these into our components so that their interfaces enable them to interact with one-another in an intuitive manner.
		
		The process of identifying the components for our system can sometimes be quite complicated, as it is not always clear where the functionality of a single component should end. To help avoid restricting ourselves too heavily regarding designating the role of our system's components, we should consider the structure, and utilities, Django has already provided us with.
	
		As discussed previously, Django is the Python web-framework in which our system is to be built upon. Therefore a series of abstractions have already been made available to us; greatly simplifying the overall task of developing the system. Given this, we are now able to apply more focus onto the design of the system's core tasks.
		
		Throughout the remainder of this section, we shall discuss the components, and their designs, in greater detail and provide reason as to why we believe the decisions we have made are beneficial.
	
	\subsubsection{Component Overview}
		As we've decided to build our system upon Django, it's also recommended that we also adopt their design-philosophy and place a high emphasis on the reusability and "pluggability" of our system's components. These philosophies are very common amongst the open-source scene; due to the ease involved with integration into other projects.
		
		Django specifies that a project is split into many smaller components, known as applications. It is often preferred that these applications are decoupled from each-other, and the project as whole, as much as possible. This makes the process of integrating an existing component into a new project much easier and far less time consuming. These applications can then be extended to work seamlessly with one-another.
		
		As mentioned previously \ref{softwarearchitectureFinalApplications}, following an extensive study into the system's current state and its requirements, we have already identified the possible applications for our system's Django project. However, we must now further delve into the specific roles of these applications.
		
		Below is a brief table which provides an outline as to the role of each component required by the system.
		
		Please note: that the following is purely a brief outline as to the functionality of each application - so some ambiguities are present.
		However, we shall break down the role of these applications later on; developing upon them in a more concise manner.
		
		\begin{itemize}
			\item \textbf{Core}:
				\begin{itemize}
					\item Unique to this system's project; not feasibly reusable.
					\item Glues together the functionality of our other applications.
					\item Provide our project with any trivial functionality - such as the view for an index page.
				\end{itemize}

			\item \textbf{\LaTeX Book}:
				\begin{itemize}
					\item Contains a parser to read LaTeX files into a Python object tree representation.
					\item An adapter capable of writing the LaTeX objects into a database.
					\item Suitable forms that staff can use to submit their own LaTeX files.
					\item Django views, and templates, capable of reading the LaTeX objects from the database and rendering them into HTML.
				\end{itemize}
				
			\item \textbf{Module}:
				\begin{itemize}
					\item Modules which student users are enrolled into.
					\item Staff users can manage modules.
					\item A module consist of various learning materials which can be browsed.
				\end{itemize} 

			\item \textbf{Homework}:
				\begin{itemize}
					\item Provides tests that student users are able to take.
					\item Staff users can analyse various aspects of the taken tests.
				\end{itemize}
			
			\item \textbf{User}:
			\begin{itemize}
				\item Typical user functionality; such as logging-in and logging-out.
				\item Allows users to be of different permission levels e.g. Students and Staff members
			\end{itemize} 
			
		\end{itemize}

	\subsubsection{The \textit{Core} Application}
		As has been repeatedly stated, one of the main motives during the design process was the idea of usability. Thankfully, Django already contains a wide range of infrastructure intended to make this motive feasibly possible.
		
		Splitting up a system into components which are decoupled from one-another is highly ideal in many situations. However, for this concept to work successfully, there must be some mechanism present which will tie the components together; combining their functionality to produce the desired outcome. This is where our \textit{Core} application comes in...
		
		The \textit{Core} application will be explicitly unique to the CAMEL project. There will be \emph{no} intention for it to be reusable in 'unrelated' projects. It's role is to couple the other applications together - so that their functionalities can become combined.
	
	\subsubsection{The \textit{\LaTeX Book} Application}
		\textit{\LaTeX Book} is to be the only application with any direct involvement with \LaTeX. It is to contain the parser which is capable of parsing \LaTeX files into a form in which Python (the primary programming language for our system) can make sense of.
		
		Along with the parser, \textit{\LaTeX Book} should also contain the Django Models which represent the relations which are to be stored within the database.
		
		However, as the \LaTeX files have no direct dependency with Django; it would be senseless to apply that dependency during our implementation of the parser. Therefore, we need to design an adapter capable of writing our "Pythonised" \LaTeX file into the database.
		
		\textit{\LaTeX Book} must also contain the functionality which allows a set group of users to submit their own \LaTeX files which are then able to be parsed and written into the database. This should also handle the case for when the uploaded \LaTeX file requires more files from the user - such as other \LaTeX documents or images.
		
		Finally, \textit{\LaTeX Book} must specify the Django views and templates that hold the capabilities to read the previously stored \LaTeX files from the database and render them into HTML - as per requested by the current visiting user.
	
	\subsubsection{The \textit{Module} Application}
		The \textit{Module} application serves quite a simple role. It allows for Staff Members to create modules in which they are able to enrol students upon. The Staff Members are then able to add various learning materials to these modules; so that the enrolled students can access them.
		
		In regards to CAMEL, the primary learning material will be the \LaTeX 'books' parsed by the \textit{\LaTeX Book} application and also the tests managed by the \textit{Homework} application.
		
		We can interpret this application almost as an arbiter for Student users over the functionality of our other applications.
		
	
	\subsubsection{The \textit{Homework} Application}
		The \textit{Homework} application should create the functionality for certain users to answer and submit forms containing their solutions for particular tests. The solutions which are submitted, for these tests, should then be analysable by particular users based upon a specified permission.
		
		The \textit{Core} application will extend upon this functionality making it so that Staff Members can add tests - which are included in the \LaTeX books parsed by the \textit{\LaTeX Book} Application - as learning materials to certain modules.
		
		It is then to make it so that a Staff Member can attach start-dates and end-dates for certain test-module combinations; so that a Student is only able to view a test and submit their solutions to it within the given time-frame.
		
	\subsubsection{The \textit{User} Application}
		The \textit{User} application is, in most likelihood, the smallest of all our system's applications. It is to only contain the functionality required for a user to login and logout of the system.
		
		Thankfully, Django already contains the ground-works which will allow us to quite easily develop a fairly robust authentication system.
		
		This application should also create for us the ability to assign certain users to a particular user-group - either Student or Staff Member. These permissions are to be required by the \textit{Core} application so it is able to configure and extend our other applications.