\documentclass{camel}

\booktitle{Test Book}
\bookauthor{Braden Marshall}
\bookversion{1.0}

\begin{document}
	Welcome to the test book!

	\chapter{First Chapter - \textbf{Bold \textit{BoldItalic}}}
		Welcome to the first chapter of our test book!

		\section{First Section}
			Welcome to the first section of our test book!
			Isn't it \emph{great}?

			\subsection{First Subsection}
				Welcome to the first subsection of our test book!

				Start verbatim environment:
				\begin{verbatim}
					This should remain as Plain Text.
				\end{verbatim}
				End verbatim environment!

			\subsection{Second Subsection}
				The following is an equation - Mathjax should do its thing...
				\begin{equation}
					x = \sqrt{16}^2
				\end{equation}

			\textit{SWEET}, end of first section!

		\section{Another Section}
			This section will be used to test a few things...
			\begin{proof}
				This could be a very \underline{complicated} proof.
			\end{proof}

		\section{Final Section}
			This is the final section!
			Lets hope everything worked!

	\chapter{Second Chapter}
		This chapter will be used to test our homeworkquiz app.

		\section{First Test}
			\begin{homework}
				Welcome to the first page of example homework.
				\begin{quiz}
					\begin{quizquestion}
						\question{What is 2^8?}
						\begin{singlechoice}
							\correctchoice{256}
							\choice{257}
							\choice{128}
							\choice{512}
						\end{singlechoice}
					\end{quizquestion}

					\begin{quizquestion}
						\question{Which countries are in Europe?}
						\begin{multiplechoice}
							\mcorrectchoice{England}
							\mcorrectchoice{France}
							\mchoice{Japan}
							\mchoice{Canada}
							\mchoice{South Africa}
						\end{multiplechoice}
					\end{quizquestion}

					\begin{quizquestion}
						\question{What is the quadratic formula?}
						\begin{mathjaxtext}
							\textanswer{x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}}
						\end{mathjaxtext}
					\end{quizquestion}
				\end{quiz}
			\end{homework}
\end{document}
