\section{Work Plan}
\subsection*{Report Two Explained}
\addcontentsline{toc}{subsection}{Gantt Charts}
The Gantt chart for the second project can be seen in Appendix 4. We have drafted a provisional plan for every team member to be clear of our individual or sub-group task. It is essential to get this plan done early so that we can start working on fragments before it is compiled as a whole. This second phase of our group project starts on Week 10 in the Autumn Semester. From Week 10 until Week 12, we started to compile a list of bugs on the CAMEL system, began to fix bugs, amend database structure, improve navigation and also test it by unit. Then, we split tasks among us to kick off the second phase of the project. Apart from that, we also met our client to get feedback of the first phase of the project. Starting in the Spring Semester, from the first until the third week, we continued towards the development of the CAMEL system. We scraped  the database structure then come out with a refreshed software architecture and data design that we found that would work better for CAMEL. Then, we further into partial implementation and testing of latest prototype that we have been working at the moment. Last sprint of the second phase of the project is to ensure that we have considered some legal, social, ethical and political issues so that we do not go against any law. This whole plan for the second project has been initially drafted in Week 12 and  confirmed in Week 1 due to some changes we have made after we stumbled upon big changes we have to made to the existing CAMEL prototype. We are aware that our plan/product roadmap needs to be revised in accordance with the  situation we faced as a group.  Since we are following Agile Software Development Management, one of the Agile Principles that we prioritised is working software, which is the primary progress of the measure.\\

\subsection*{Report Three Explained}

The Gantt chart for the second project can be seen in Appendix 5. We plan to start development for our third report at the start of Week 4, after report 2 has been submitted. We have allocated from the 15/02 until 15/04 to complete all physical relevant requirements within our software. As our project is heavily dependent on fixing and amending existing code, we feel allocating a large time to this will help us all complete and implement the required requirements.\\

From the 18/04 until 26/04, we aim to complete the development of the third report, having completed all the software implementations we can then develop justifications of our actions and produce a write up. Within the weeks of developing the third report, we will also produce a presentation of our working software. We will include what we have developed, how we met the client's requirements, with the working software and we will then be prepared to present this in week 12. Relating to our original plan in report 1, report 3 will aim to cover the requirements of maintainable code, admin and developer documentation where relevant, however most user documentation will minimal as we aim to make the use of the camel website to be self explanatory. It will also include testing frameworks, comparisons of users answers, PEP8 standardisation, authors page, methods of checking and comparing students answers, deadlines for students assignment submissions, functionality for the student to only see the modules they are enrolled on, ease of use will be consistent throughout the software and it will have security permissions to prevent unauthorised access. All stakeholders requirements and needs will be completed by report 3.\\

\subsection*{Weekly Work Plan}
\addcontentsline{toc}{subsection}{Weekly Work Plan}

In order to manage our group, we discovered that a clear concise weekly work plan with internal milestones was a easier method to keep on track of milestones within the project. Each member had access to a copy of the work plan and it was confirmed which tasks needed to be completed before another task began, or what could run in parallel within the Gantt Charts activities. We have attached copies of the weekly work plans for report 2 and report 3 in the appendices. They allow us to monitor meetings with the group and the client to ensure we are consistent with the delivery of our software. (See Appendix 6)\\

\subsection*{Feasibility of Work Plan}

We all aim to follow the work plan accordingly, to achieve the projected results. By ensuring internal milestones are met we can ensure each task is continued thereafter, as some elements such as fixing all the current code in place needs to be completed before amending the code to adhere to requirements. We need to ensure the CaMeL system is in working state and we all know what the current code does, before we can alter existing code and implement features to increase usability for stakeholders.\\

So far the Gantt chart has been feasible and we have adhered to the deadlines and milestones that were set from the first Gantt chart development. We have however amended the Gantt chart to meet to needs of future requirements, by setting milestones of tasks that need to be completed by report 2 and report 3. By adding these features to our Gantt chart we can ensure the feasibility of our work plan is continued by viewing future deadlines, and from the experience of report 1 we are on target to meet all the set milestones to complete our project in due course.\\

The work plan also aids us in monitoring the workload of each member, to ensure each member has a task to complete and is contributing to the project.

\subsection*{Risk Assessment and Risk Mitigation}
\addcontentsline{toc}{subsection}{Risk Assessment and Risk Mitigation}

The use of risk mitigation can be used for minimising risks. In our first report we included an in depth risk map that considered all possible risks that could occur during the duration of our project. We included controls to manage the risk in report 1 but we also have strategies in place to minimise the effects should they still happen to occur. We have created contingencies for the risks as follows:\\

\input{workplan/key}

 In order to assess the risks of our project we included the use of a risk map. We identified the risk that could occur in the duration of our project and then have put strategies in place should they do occur. We included the calculations of the total risk by measuring the likelihood of the event occurring, against the impact it would have should it occur. The strategies in place helps us to maintain the project goals and control the overall risk. We followed the colour schemes of the risk map so it is more visually appealing and clearer to assess how the controls we implemented help. \\
 
\input{workplan/risk}

